\thetitle

### 2021-05-11 paper/paper.tex
update

\begin{abstract}
  % teilw. von IJPR paper uebernommen
  An essential task in manufacturing planning and control is to determine when to release orders to
  the shop floor. One key parameter is the lead time which is the planned time that elapses between
  the release of an order and its completion. Lead times are usually determined based on the
  measured duration orders take to traverse the production system, i.e.\@ the flow times.
  Traditional order release models assume static lead times, although it has been shown that they
  should be set dynamically to be able to react to the dynamic operational characteristics of
  production system. Therefore, we present an order release model which sets lead times dynamically
  by using an reinforcement learning approach. This algorithm is designed especially for
  applications with high variability and periodic feedback to the agent. Therefore, this paper aims
  at providing a proof-of-concept for the proposed algorithm. Therefore, we compare our method on a
  three-stage flow-shop simulation model not only to static order release techniques, but also to
  the commonly used deep Q-Learning algorithm. The results show that the both reinforcement learning
  agents have room for improvement for queuing systems with low variability, that our proposed
  method usually outperforms deep Q-Learning and finally for systems with high variability that the
  proposed reinforcement learning algorithm performs very well.
  %
  % We use a  to compare the algorithm
  % to % and show that our approach outperforms
  % well-known order release mechanisms. We show that in the current version our proposed model using
  % reinforcement learning outperforms some, but not all other tested approaches.
  % EVTL: especially for scenarios with...
  \keywords{operations research, production planning, order release, machine learning, reinforcement
    learning}
\end{abstract}

@@

\paragraph*{Neural Network Setup.}
%
Due to the vast possibilities the neural network architecture was manually optimised, starting with
less stochastic systems and aiming for a coffin shape that can be used in all setups. During this
process we constantly adapted and reevaluated the best network on various production system
configurations. The resulting architecture depends on the number of features \(\anninp\) and the
number of output nodes \(\annout\), which itself depends on the number of actions
\(\acts = \size{\States}\), the independent agent configuration, and the number of functions that
are approximated. For the later, in case of \ARA{} this is \(2\), as we represent both functions
\(\X^\pol_{\gamma_{0}}\) and \(\X^\pol_{\gamma_{1}}\) with the same neural network, while deep
Q-Learning \citep[cf.][]{mnih2015human} only approximates the function \(Q_{\gamma}^\pol\).
%
The resulting feedforward deep ANN architecture is given as %
\(\anninp %
\rightarrow 1.75 \anninp % \rightarrow \relu
\rightarrow 1.5 \anninp % \rightarrow \relu
% \rightarrow 2 \annout % \rightarrow \relu
\rightarrow \annout %
% \rightarrow   \leakyTanh%
\), where each arrow symbolises a fully-connected layer with a leaky rectified linear unit
(\(\relu\)) as activation function, which leaks values smaller than \(0\) with rate \(0.02\).
%
Note
that we explicitly do not use an output activation function. The idea is that we do not want to
restrict the approximations to values inside this range. This is especially important for
Q-Learning, as the range of the state values are difficult to forecast.
%
The actual values \(\anninp\) and \(\annout\) depend on the used algorithm. In our case using 6
independent agents we gain \(\anninp=324\) and \(\annout=36\).
%
% SpecFullyConnected 324 567 :=> SpecLeakyRelu (567,1,1) :=> SpecFullyConnected 567 486 :=>
% SpecLeakyRelu (486,1,1) :=> SpecFullyConnected 486 36 :=> SpecReshape (36,1,1) (18,2,1) :=>
% SpecNNil2D18x2
%

>>>>

\begin{abstract}
  % teilw. von IJPR paper uebernommen
  An essential task in manufacturing planning and control is to determine when to release orders to
  the shop floor. One key parameter is the lead time which is the planned time that elapses between
  the release of an order and its completion. Lead times are usually determined based on the
  measured duration orders take to traverse the production system, i.e.\@ the flow times.
  Traditional order release models assume static lead times, although it has been shown that they
  should be set dynamically to be able to react to the dynamic operational characteristics of
  production system. Therefore, we present an order release model which sets lead times dynamically
  by using an reinforcement learning approach. This algorithm is designed especially for
  applications with high variability and periodic feedback to the agent. Therefore, this paper aims
  at providing a proof-of-concept for the proposed algorithm. Therefore, we compare our method on a
  three-stage flow-shop simulation model not only to static order release techniques, but also to
  the commonly used deep Q-Learning algorithm. The results show that both reinforcement learning
  agents have room for improvement for queuing systems with low variability, that our proposed
  method usually outperforms deep Q-Learning and finally for systems with high variability that the
  proposed reinforcement learning algorithm performs very well.
  %
  % We use a  to compare the algorithm
  % to % and show that our approach outperforms
  % well-known order release mechanisms. We show that in the current version our proposed model using
  % reinforcement learning outperforms some, but not all other tested approaches.
  % EVTL: especially for scenarios with...
  \keywords{operations research, production planning, order release, machine learning, reinforcement
    learning}
\end{abstract}

@@

\paragraph*{Neural Network Setup.}
%
Due to the vast possibilities the neural network architecture was manually optimised, starting with
less stochastic systems and aiming for a coffin shape that can be used in all setups. During this
process we constantly adapted and reevaluated the best network on various production system
configurations. The resulting architecture depends on the number of features \(\anninp\) and the
number of output nodes \(\annout\), which itself depends on the number of actions
\(\acts = \size{\States}\), the independent agent configuration, and the number of functions that
are approximated. For the later, in case of \ARA{} this is \(2\), as we represent both state-action
value functions \(\X^\pol_{\gamma_{0}}\) and \(\X^\pol_{\gamma_{1}}\) with the same neural network,
while deep Q-Learning \citep[cf.][]{mnih2015human} only approximates the function
\(Q_{\gamma}^\pol\).
%
The resulting feedforward deep ANN architecture is given as %
\(\anninp %
\rightarrow 1.75 \anninp % \rightarrow \relu
\rightarrow 1.5 \anninp % \rightarrow \relu
% \rightarrow 2 \annout % \rightarrow \relu
\rightarrow \annout %
% \rightarrow   \leakyTanh%
\), where each arrow symbolises a fully-connected layer with a leaky rectified linear unit
(\(\relu\)) as activation function, which leaks values smaller than \(0\) with rate \(0.02\).
%
Note
that we explicitly do not use an output activation function. The idea is that we do not want to
restrict the approximations to values inside this range. This is especially important for
Q-Learning, as the range of the state values are difficult to forecast.
%
The actual values \(\anninp\) and \(\annout\) depend on the used algorithm. In our case using 6
independent agents we gain \(\anninp=324\) and \(\annout=36\).
%
% SpecFullyConnected 324 567 :=> SpecLeakyRelu (567,1,1) :=> SpecFullyConnected 567 486 :=>
% SpecLeakyRelu (486,1,1) :=> SpecFullyConnected 486 36 :=> SpecReshape (36,1,1) (18,2,1) :=>
% SpecNNil2D18x2
%
